MCTS Applied to Co-operative Problems

### 2015-07-02 Report/ceec.tex
Work on the reports
Work on things

\title{MCTS Applied To Co-operative Problems}

@@

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Uniform Cost applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}

@@

\subsection{AI Controllers}
\subsubsection{Random}
The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
\subsubsection{Keyboard}
The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
\subsubsection{\gls{mcts}}
The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border. No knowledge about the game is provided and the assumption is made that the other player will play randomly. The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms). This greatly improves the ability of \gls{mcts} to make informed decisions. The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
\subsubsection{A Star}
An intelligent agent was required that could provide comparison to how the MCTS is performing. A Star was selected and written to view the problem as selecting the shortest path of actions that would result in reaching the goals.

>>>>

\title{MCTS Applied to Co-operative Problems}

@@

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Uniform Cost applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}
\newacronym{ga}{GA}{Genetic Algorithm}

@@

\subsection{AI Controllers}
\subsubsection{Random}
The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
\subsubsection{Keyboard}
The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
\subsubsection{\gls{mcts}}
The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border. No knowledge about the game is provided and the assumption is made that the other player will play randomly. The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms). This greatly improves the ability of \gls{mcts} to make informed decisions. The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
\subsubsection{A*}
An intelligent agent was required that could provide comparison to how the MCTS is performing. A Star was selected and written to view the problem as selecting the shortest path of actions that would result in reaching the goals.
\subsubsection{Macro Action Genetic Algorithm}
The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
\subsubsection{Variable Macro Action Genetic Algorithm}
